Multi-Task Temporal and Spatial Networks for Precise Event Spotting in Volleyball Videos\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-10-31 paper.tex
refine model architecture description and add TODOs for future enhancements

@@

\end{itemize}
\subsubsection{Spatio-Temporal Prediction Heads}
The model predicts event classes and spatial coordinates through distinct heads, each optimized with a multi-task loss function that balances temporal and spatial prediction objectives. The event class head outputs a vector of logits \(\hat{y}_t\) representing the predicted class probabilities for each event, while the spatial head outputs a vector of coordinates \(\hat{s}_t\) representing the predicted spatial location of the event within the frame. By jointly optimizing these heads, the model can effectively learn spatio-temporal features and produce accurate predictions for both event timing and location.
\subsubsection{Multi-task Loss Function}
The model is trained with a multi-task loss function that balances temporal and spatial prediction objectives, ensuring that the model learns to predict both when and where key events occur. The loss function is defined as the sum of two terms: a temporal classification loss and a spatial regression loss. The temporal classification loss penalizes errors in event class predictions

>>>>

% TODO: Add a Math formula for the model architecture: ...

@@

\end{itemize}
\subsubsection{Spatio-Temporal Prediction Heads}
% TODO: Refine this 
The model predicts event classes and spatial coordinates through distinct heads, each optimized with a multi-task loss function that balances temporal and spatial prediction objectives. The event class head outputs a vector of logits \(\hat{y}_t\) representing the predicted class probabilities for each event, while the spatial head outputs a vector of coordinates \(\hat{s}_t\) representing the predicted spatial location of the event within the frame. By jointly optimizing these heads, the model can effectively learn spatio-temporal features and produce accurate predictions for both event timing and location.
\subsubsection{Multi-task Loss Function}
The model is trained with a multi-task loss function that balances temporal and spatial prediction objectives, ensuring that the model learns to predict both when and where key events occur. The loss function is defined as the sum of two terms: a temporal classification loss and a spatial regression loss. The temporal classification loss penalizes errors in event class predictions
